### 2016-12-02 dissertation/intro.tex
dissertation v2:part intro completed

\chapter{Introduction}
\label{ch:intro}
With the increasing size of integrated
circuits, sequential circuit designers face complicated problems of
design errors in specification models and implementations. These
errors are usually modeled as ``bad" states, and the
circuits/functional components are modeled as finite state machines
(FSMs). Once state reachability is analyzed, the existence of errors
can be identified by checking whether ``bad" states are {\it
  reachable} from certain initial states. Temporal logic {\it model
  checking} (MC) formulations and solvers are often used for this
purpose. Once the designs and specification models are validated using
model checking, optimized implementations of sequential circuits are
synthesized. A subsequent problem then needs to be solved to prove
that the sequential circuit implementations are equivalent to the
original specification models, i.e. {\it Sequential Equivalence
  Checking   (SEC)}.

Reachability analysis forms the backbone of most sequential
verification techniques. As the state-space of FSMs increases,
reachability analysis forms a fundamental bottleneck in sequential
verification. Contemporary approaches employ various techniques to
overcome this state-explosion problem: i) Bounded model checking
\cite{bitlevel1} traverses the FSMs for a fixed number of steps $k$
($k$-BMC) to check whether a property violation can occur in $k$ or
fewer steps. ii) Analyze over-approximations (or {\it abstractions})
of the state-space. Abstraction proves properties on the system by
first simplifying it, and when the abstraction does not satisfy the
same properties as the original one, a process of refinement is
needed. {\it Craig interpolants} \cite{craig-interpolate}
\cite{pudlak:ci} are used as a means of abstraction and reachability
analysis for linear temporal logic (LTL) model checking
\cite{mcmillan:interpolation}. Similarly, counterexample guided
abstraction refinement (CEGAR) \cite{cegar-journal} uses proofs of
unsatisfiability (UNSAT cores) to refine the abstractions. iii) the
recent breakthrough method of \cite{bradley:pdr} where the set of
over-approximations to forward reachable states are refined with
inductive constraints -- property directed reachability (PDR).

@@

There are several advantages in exploiting word-level information for
verification. A number of designs have  their
datapaths and/or system-level models described as word-level RTL
models.  Exploiting word-level instead of bit-level information is one
way of abstraction -- a key technique to reduce the state space of a
FSM. It has the effect of combining sets of states with similar 
properties. During reachability analysis, if we use bit-level
variables to  represent the states, the representations may become too
large to handle. However, when a ``bundle" of bit-level variables are
represented as {\it only one word-level variable}, the set of
reachable states can be represented by a  word-level constraint
expression; which may lower verification complexity.

{\bf Overall Research Objective:} In this proposal we investigate a
set of new, promising approaches for {\it word-level representation,
reachability analysis and abstraction} with applications to SEC,
$k$-BMC and abstraction-based unbounded LTL model checking
(A-UMC). Our techniques operate at the word-level and they are based
largely on the concepts from {\it algebraic geometry}.

For word-level SEC, we are given two designs, or their corresponding
Mealy/Moore FSMs ${\mathcal{M}}_1,{\mathcal{M}}_2$, along with their
initial starting states $S_0^1,S_0^2$. We wish to prove the absence of
a sequence of inputs (string) that distinguishes the initial
states \cite{coudert:iccad90}
\cite{coudert1990verification}. Fundamentally, this requires 
the construction of a product machine; and the main research problem
relates to that of performing {\it FSM traversal \cite{touati:iccad90}
but  at the word-level}. Analogously, in the case of MC, the problem
is setup w.r.t. a FSM $\mathcal{M}$, a set of initial states $S_0$ and
a set of property states $p$. Techniques are to be researched that
verify that there exist no sequence of transitions from an initial
state to a non-property state (``bad'' state). These problems have to
be solved in the context of word-level verification -- i.e. data
representation, abstraction (Craig interpolation, UNSAT cores) and
algorithm execution has to be carried out at word-level.

Boolean functions with $k$-bit inputs and $k$-bit outputs 
$f: \B^k \rightarrow \B^k,\B = \{0, 1\}$ can be construed as functions
$f: \Fkk \rightarrow \Fkk$. It is well-known that over the finite
field ($\Fq$) of  $q$ elements, {\it every function} $f: \Fq
\rightarrow \Fq$ is a polynomial function \cite{ff:1997}. Moreover,
there exists a unique canonical polynomial $\FF$ that describes $f$.
This implies that one can derive a {\it  canonical, polynomial
  abstraction} of the function as $Z = \FF(A)$ where $Z, A$ are
word-level symbols representing $k$-bit operands. The concept also
generalizes to functions with different input/output bit-vector sizes,
i.e. functions of the type $f: \B^n \rightarrow \B^m$, modeled as
polynomials over $f:{\mathbb{F}}_{2^k} \rightarrow
{\mathbb{F}}_{2^k}$, where $k=LCM(n,m)$ \cite{ff:1997}.  
This implies that the FSM's transition relations can be
represented as polynomial functions (ideals) in $\Fkk$, and values of
state variables can be represented as solutions to these polynomials
(variety of the ideal). Subsequently, the ideal-variety correspondences
in algebraic geometry can be applied to implement symbolic reasoning
about state reachability. Moreover, as ${\mathbb{F}}_2 \subset \Fkk$,
our model provides a single, unified and bit-precise representation
for both bit-level (${\mathbb{F}}_2$) and word-level ($\Fkk$)
constraints.

{\bf The core focus of this research:} The use of algebraic geometry
for sequential circuit verification and symbolic model checking has
been presented before. Avrunin presented the
concept of symbolic MC using algebraic geometry in
\cite{Avrunin:CAV}. Later, in \cite{vardi-iasted07}, Vardi presented
GB-algorithms for CTL, LTL and 
bounded MC over Boolean rings. However, these approaches are a
straight-forward transformation of the problem to {\it bit-level}
Boolean GB engines which are used in lieu of BDDs or SAT solvers. All
the concepts of word-level reachability, abstraction-refinement using
interpolation or UNSAT cores, etc., that we desire was not the focus of
\cite{Avrunin:CAV} \cite{vardi-iasted07}.

In this research, we will focus on three specific research problems: 
\begin{enumerate}
\item How to perform reachability analysis at the word-level? This
  of course forms the foundation for word-level SEC and MC.
\item What is the analog of Craig interpolation in an algebraic
  geometry setting (theoretical challenge), and how can we compute
  various interpolants using GB-engines efficiently (practical
  implementation)? This will enable word-level abstraction of the
  state-space. 
\item Explore the concept, and the computation, of unsatisfiable (UNSAT)
  cores of  a set of polynomials. Many abstraction-refinement
  techniques make use of UNSAT cores of CNF-formulas in MC. Therefore,
  our investigation of UNSAT cores of polynomial ideals will enable
  similar applications at word-level. 
\end{enumerate}

\section{Design, Test and Verification of Modern Sequential Circuit Components}\section{Hardware Design and Verification Overview}
The typical design flow of a hardware system, 
as shown in Fig. \ref{fig:cadflow}, starts with a hardware system 
specification, which describes the necessary functions and parameters that 
the system must perform and adhere to. The specification is typically
modelled using a transaction-level model (\emph{TLM}), which describes 
communication details between large circuit modules. 
The TLM is then translated 
into a register-transfer-level (\emph{RTL}) description, which is composed of abstracted, 
interconnected circuit blocks that compose the entire system. RTL is 
typically implemented 
in hardware description languages (\emph{HDL}) such as Verilog and VHDL, 
which are the most popular choices in the industry.
Next, the RTL is optimized and converted into a \emph{netlist}, i.e. a large 
collection of small physical blocks (MOSFET, Boolean logic gates, etc.) and 
the inter-connections (wires) between them. 
Lastly, the netlist is further optimized and then mapped onto a physical space 
on a chip, which is then sent off for fabrication. This entire design flow
is automated by Computer-Aided Design (\emph{CAD}) tools.

{
\begin{figure}[h]
\centerline{
\includegraphics[width=0.5\textwidth]{./figures/designFlow}
}
\caption{Typical hardware design flow.}
\label{fig:cadflow}
\end{figure}
}

%\subsection{The Hardware Verification Imperative}
When moving from one abstraction level of the hardware design process to the 
next, an important issue arises: how can one ensure that the functionality of 
the optimized design matches original spec? 
Bugs in hardware design which are 
not caught early can have costly effects later, such as the need for a 
redesign. Bugs in arithmetic circuits can be especially catastrophic.
One infamous example is the 1994 floating point division (FDIV)
bug that affected the Intel Pentium chip \cite{nicely:FDIV}, 
and subsequently cost the company \$475 million because it was  
discovered after the chip's release. In another more fatal case, during the
Gulf war, an American Patriot Missile battery failed to intercept an incoming
enemy missile due to an arithmetic error \cite{arnold:patriot}.
Since hardware bugs can have significant consequences, 
there has been extensive work in field of hardware verification to find and
eliminate bugs prior to fabrication.

The two main methodologies used in hardware verification are simulation and 
formal verification. \emph{Simulation} checks correctness by applying exhaustive 
assignments to the circuit inputs and verifying correctness of the output. 
This ensures that the circuit performs as designed under all possible 
inputs. Such exhaustive testing is quite effective for smaller circuits. 
However, as the size of the circuit increases, it becomes 
computationally infeasible to simulate all possible test vectors. This is the 
case with Galois field arithmetic circuits, which are commonly very large in 
real-world applications. Often for such large circuits, simulations of a smaller and more 
manageable subset of test vectors are employed to catch bugs. While these tests
can increase confidence in the correctness of the design,  
{\it they do not guarantee correctness} since every data-flow of the design hasn't
been analyzed.
%Such is the case with large Galois field arithmetic circuits, so we instead 
%focus on formal verification.

\section{Formal Verification}
Instead of simulating input vectors, \emph{formal verification} utilizes 
mathematical theory to reason about the correctness of hardware designs.
%which overcomes some limitations of simulation. 
Formal verification has two main forms: property checking and equivalence 
checking.

@@

\section{Importance of Word-level Abstraction}
Most formal verification techniques can benefit from word-level abstractions 
of the circuits they verify.
Abstraction is defined as state-space reduction, i.e{\text . }abstraction
reduces state-space by mapping the set of states of a system to a smaller 
set of states. Because the new representation contains fewer states, it
is easier to comprehend and thus easier to use. 
Word-level abstraction focuses specifically on abstracting a word-level
representation of a circuit out of a bit-level representation. For example,
a bit-level representation of an integer multiplier is represented by a
collection of Boolean inputs and outputs, whereas a word-level
abstraction hides the underlying logic and represents the circuit as two 
integer inputs and one integer output, e.g. $Z=A\cdot B$. As the bit-size of the
multiplier increases, the logical implementation of the multiplier grows (typically
exponentially) while the word-level abstraction stays the same.

@@

Finally, abstractions can also be applied to detect malicious 
modifications to a circuit, potentially inserted as a hardware trojan horse.
Hardware trojans, a relatively new security concern in the hardware 
industry, use certain techniques to add incorrect behavior to a 
design. 
This behavior is only activated under certain rare circumstances that only 
the mal-intent designer has knowledge of.
The behavior is purposely hidden and is very difficult to encounter during 
simulation of the design. A manufactured chip with a subsystem 
that contains a hardware trojan could compromise the entire system in which 
it is used.
In some hardware trojan cases, formal verification techniques may be applied 
to catch a bug in a design and provide a counter-example which exercises it. 
However, it can be difficult to tell whether the bug in the design was 
introduced intentionally of not. On the other hand, word-level abstractions 
of bit-level circuits {\it effectively reverse-engineer the true function 
implemented by the circuit}, which could be used to determine the designer's 
true intention.

\section{Objective, Motivation and Contribution of this Dissertation}
\subsection{Word-level Reachability and FSM Traversal}
\subsection{Application to Galois Field Multipliers}
\subsection{Abstractions for Sequential Circuits}
\subsection{Other Applications}

\section{Dissertation Organization}
{\bf Proposal Organization:} The rest of the proposal is organized as
follows: The following Subsection describes the intellectual merit of
the proposed work.  Section \ref{sec:prelim} covers preliminary
concepts and notation. Section \ref{sec:reach} describes the basic
concept of word-level FSM traversal and the research problems to
investigate. Section \ref{sec:craig} explores the algebraic geometry
analog of Craig Interpolants. Section \ref{sec:core} describes
algorithmic techniques to derive UNSAT cores of polynomial
ideals. Section \ref{sec:plan} puts the whole research in perpective,
by demonstrating  with the help of an example how abstraction via
unsat cores in algebraic geometry can simplify BMC. 
Section \ref{sec:impact} addresses the broader impact of the
proposed activity and concludes the proposal.

>>>>

\chapter{Introduction}
\label{ch:intro}
With the increasing size of integrated
circuits, sequential circuit designers face complicated problems of
design errors in specification models and implementations. These
errors are usually modeled as ``bad" states, and the
circuits/functional components are modeled as finite state machines
(FSMs). Once state reachability is analyzed, the existence of errors
can be identified by checking whether ``bad" states are {\it
  reachable} from certain initial states. Temporal logic {\it model
  checking} (MC) formulations and solvers are often used for this
purpose. Once the designs and specification models are validated using
model checking, optimized implementations of sequential circuits are
synthesized. A subsequent problem then needs to be solved to prove
that the sequential circuit implementations are equivalent to the
original specification models, i.e. {\it Sequential Equivalence
  Checking   (SEC)}. When the specification is given as an arithmetic function
which canonically represents the circuit, then the problem 
becomes {\it functional verification} of sequential arithmetic circuits.

Reachability analysis forms the backbone of most sequential
verification techniques. As the state-space of FSMs increases,
reachability analysis forms a fundamental bottleneck in sequential
verification. Contemporary approaches employ various techniques to
overcome this state-explosion problem:

\begin{enumerate}[{1)}]
\item Bounded model checking
\cite{bitlevel1} traverses the FSMs for a fixed number of steps $k$
($k$-BMC) to check whether a property violation can occur in $k$ or
fewer steps.  
\item Analyze over-approximations (or {\it abstractions})
of the state-space. Abstraction proves properties on the system by
first simplifying it, and when the abstraction does not satisfy the
same properties as the original one, a process of refinement is
needed. For example, counterexample guided
abstraction refinement (CEGAR) \cite{cegar-journal} uses proofs of
unsatisfiability (UNSAT cores) to refine the abstractions.
\item The recent breakthrough method of \cite{bradley:pdr} where the set of
over-approximations to forward reachable states are refined with
inductive constraints -- property directed reachability (PDR). 
\end{enumerate}

@@

For word-level SEC, we are given two designs, or their corresponding
Mealy/Moore FSMs ${\mathcal{M}}_1,{\mathcal{M}}_2$, along with their
initial starting states $S_0^1,S_0^2$. We wish to prove the absence of
a sequence of inputs (string) that distinguishes the initial
states \cite{coudert:iccad90}
\cite{coudert1990verification}. Fundamentally, this requires 
the construction of a product machine; and the main research problem
relates to that of performing {\it FSM traversal \cite{touati:iccad90}
but  at the word-level}. Analogously, in the case of MC, the problem
is setup w.r.t. a FSM $\mathcal{M}$, a set of initial states $S_0$ and
a set of property states $p$. Techniques are to be researched that
verify that there exist no sequence of transitions from an initial
state to a non-property state (``bad'' state). These problems have to
be solved in the context of word-level verification -- i.e. data
representation, abstraction using UNSAT cores and
algorithm execution has to be carried out at word-level.

\section{Hardware Design and Verification Overview}
Following the Moore's law, the level of integration on modern VLSI becomes very high, 
such that a single digital VLSI design can implement a true system-level component.
The design process also evolves from manual design with little validation, to 
a formal 3-step procudure which needs collaboration of team with large number of 
engineers. The 3 major steps are: 1) Design, which is to specify and enter the design intent;
2) Implement, which is to refine the design through all phases with the assistance of Computer-Aided-Design (CAD)
tools; 3) Verify, which is to verify the correctness of design and implementation.

Nowadays the verify step is usually completed by a team with specialities on test, verification and validation of 
circuits. This step is also automated as an indispensable part of CAD tools, when circuit synthesis is performed. 
Figure \ref{fig:designflow} shows the typical synthesis flow, which covers all procudures starting from 
register-transfer-level (RTL) description (using hardware design languages, i.e. HDL) to  the 
physical design on silicon (depicted by the layout). The objective of verification in synthesis is 
to ensure the implementation is consistent with the original design intent. Verification is 
an important quality control measure before sending design layout to the VLSI foundaries.
Considering the high cost of fabrication, any faults and errors in the design will bring considerable 
waste of funds for the designers. On the other hand, all aspects of the society increasingly depend on 
the stability and accuracy of digital VLSI circuits, even small flaws or short-time failures can cause 
huge loss, especially in medical applications, military facilities and financial systems.
Therefore, it is of utmost importance to verify the correctness of VLSI designs.

One way to perform the verification is called {\it simulation}. It is defined as the collage of all circuit validation 
methods which apply stimulations on the inputs of circuit model and verify correctness of the outputs.
However, simulation is not a complete solution to circuit verification problems. In modern designs with 
large number of logic components and complicated architecures, it is impractical to simulate all possible 
test vectors. Usually only test vectors that correspond to typical failures are selected in simulation, which 
cannot cover unexpected failure patterns caused by special inputs. The notorious Intel FDIV bug \cite{nicely:FDIV}
is a good example when simulation fails. Failure occurs when only 5 entries in an $84\times 16$ look-up table
(LUT) are activated,  which is rarely used in most divisions. Because of the limitation of simulation,  
test engineers from Intel failed to detect the bug,  which brought $\$475$ million dollors recalling bill
for the company. Thus,  new methods that can guarantee the correctness of the design are necessary to be explored.

{
\begin{figure}[h]
\centerline{
\includegraphics[width=0.7\textwidth]{newfig/designflow.eps}
}
\caption{Typical hardware design flow}
\label{fig:designflow}
\end{figure}
}

\section{Formal Verification}
% TODO this part require less modifications
Another method developed besides simulation is \emph{formal verification}, it utilizes 
mathematical theory to reason about the correctness of hardware designs.
Formal verification can provide $100\%$ fault coverage from 2 aspects. On the one hand,  it formalize properties
for the circuit model which are irrelevant to specific input signals,  and prove them mathematically.
On the other hand,  it adopts formal languages to strictly describe the design intents and detailed implementation, 
and deduces circuit function from the implementation. These descriptions are named as {\it specifications}.
Formal verification has two main forms: property checking and equivalence 
checking.

@@

\section{Importance of Word-level Abstraction}
Most formal verification techniques can benefit from word-level abstractions 
of the circuits they verify.
There are several advantages in exploiting word-level information for
verification. A number of designs have  their
datapaths and/or system-level models described as word-level RTL
models.  Exploiting word-level instead of bit-level information is one
way of abstraction -- a key technique to reduce the state space of a
FSM. It has the effect of combining sets of states with similar 
properties. During reachability analysis, if we use bit-level
variables to  represent the states, the representations may become too
large to handle. However, when a ``bundle" of bit-level variables are
represented as {\it only one word-level variable}, the set of
reachable states can be represented by a  word-level constraint
expression; which may lower verification complexity.

% Abstraction is defined as state-space reduction, i.e{\text . }abstraction
% reduces state-space by mapping the set of states of a system to a smaller 
% set of states. Because the new representation contains fewer states, it
% is easier to comprehend and thus easier to use. 
% Word-level abstraction focuses specifically on abstracting a word-level
% representation of a circuit out of a bit-level representation. For example,
% a bit-level representation of an integer multiplier is represented by a
% collection of Boolean inputs and outputs, whereas a word-level
% abstraction hides the underlying logic and represents the circuit as two 
% integer inputs and one integer output, e.g. $Z=A\cdot B$. As the bit-size of the
% multiplier increases, the logical implementation of the multiplier grows (typically
% exponentially) while the word-level abstraction stays the same.

@@

% Finally, abstractions can also be applied to detect malicious 
% modifications to a circuit, potentially inserted as a hardware trojan horse.
% Hardware trojans, a relatively new security concern in the hardware 
% industry, use certain techniques to add incorrect behavior to a 
% design. 
% This behavior is only activated under certain rare circumstances that only 
% the mal-intent designer has knowledge of.
% The behavior is purposely hidden and is very difficult to encounter during 
% simulation of the design. A manufactured chip with a subsystem 
% that contains a hardware trojan could compromise the entire system in which 
% it is used.
% In some hardware trojan cases, formal verification techniques may be applied 
% to catch a bug in a design and provide a counter-example which exercises it. 
% However, it can be difficult to tell whether the bug in the design was 
% introduced intentionally of not. On the other hand, word-level abstractions 
% of bit-level circuits {\it effectively reverse-engineer the true function 
% implemented by the circuit}, which could be used to determine the designer's 
% true intention.

\section{Objective, Motivation and Contribution of this Dissertation}
This research proposes a
set of new, promising approaches for {\it word-level representation,
reachability analysis and abstraction} with applications to SEC, sequential GF
arithmetic functional verification and 
$k$-BMC with abstraction refinement. Our techniques operate at the word-level and they are based
largely on the concepts from {\it algebraic geometry}.

\subsection{Motivating Application}

The use of algebraic geometry
for sequential circuit verification and symbolic model checking has
been presented before. Avrunin presented the
concept of symbolic MC using algebraic geometry in
\cite{Avrunin:CAV}. Later, in \cite{vardi-iasted07}, Vardi presented
GB-algorithms for CTL, LTL and 
bounded MC over Boolean rings. However, these approaches are a
straight-forward transformation of the problem to {\it bit-level}
Boolean GB engines which are used in lieu of BDDs or SAT solvers. All
the concepts of word-level reachability, abstraction-refinement using
interpolation or UNSAT cores, etc., that we desire was not the focus of
\cite{Avrunin:CAV} \cite{vardi-iasted07}.

Boolean functions with $k$-bit inputs and $k$-bit outputs 
$f: \B^k \rightarrow \B^k,\B = \{0, 1\}$ can be construed as functions
$f: \Fkk \rightarrow \Fkk$. It is well-known that over the finite
field ($\Fq$) of  $q$ elements, {\it every function} $f: \Fq
\rightarrow \Fq$ is a polynomial function \cite{ff:1997}. Moreover,
there exists a unique canonical polynomial $\Func$ that describes $f$.
This implies that one can derive a {\it  canonical, polynomial
  abstraction} of the function as $Z = \Func(A)$ where $Z, A$ are
word-level symbols representing $k$-bit operands. The concept also
generalizes to functions with different input/output bit-vector sizes,
i.e. functions of the type $f: \B^n \rightarrow \B^m$, modeled as
polynomials over $f:{\mathbb{F}}_{2^k} \rightarrow
{\mathbb{F}}_{2^k}$, where $k=LCM(n,m)$ \cite{ff:1997}.  
This implies that the FSM's transition relations can be
represented as polynomial functions (ideals) in $\Fkk$, and values of
state variables can be represented as solutions to these polynomials
(variety of the ideal). Subsequently, the ideal-variety correspondences
in algebraic geometry can be applied to implement symbolic reasoning
about state reachability. Moreover, as ${\mathbb{F}}_2 \subset \Fkk$,
our model provides a single, unified and bit-precise representation
for both bit-level (${\mathbb{F}}_2$) and word-level ($\Fkk$)
constraints.

\subsection{Dissertation Contributions}
% TODO revise this to contributions
In this dissertation, we focus on sequential circuit verification problems and 
propose solutions consisting of three main contributions: 
\begin{enumerate}[{1)}]
\item A method to perform reachability analysis at the word-level. 
	The given FSM is modeled as a system of polynomials over finite field,
	where the state space is mapped to its solution space.
	Our proposed algorithm utilize concepts in algebraic geometry including ideals and varieties.
	It also forms the foundation for word-level SEC and MC by enabling word-level abstraction of the
  state-space.
\item Using the theory of FSM traversal, we apply the algorithm to verify the 
function of sequential GF arithmetic circuits. Our proposed approach uses GB-engines efficiently 
and can verify sequential multipliers with 162-bit datapaths.
\item We explore the concept, and the computation, of unsatisfiable (UNSAT)
  cores of  a set of polynomials using Gr\"obner bases calculation. We apply the UNSAT core extraction 
  to abstraction-refinement
  techniques such as bounded model checking (BMC). 
\end{enumerate}

\section{Dissertation Organization}
The rest of the dissertation is organized as
follows: Chapter \ref{ch:prev} reviews previous work, and analyzes their drawbacks with respect to 
the word-level sequential verification problem.
Chapter \ref{ch:prelim_GF} covers preliminary
concepts and notation on finite fields, and the methodology about design of multipliers in finite fields.
Chapter \ref{ch:ideals} provides a theoretical background of algebraic geometry and Gr\"obner bases.
Chapter \ref{ch:reacha} describes the basic
concept of word-level FSM traversal and introduces our proposed word-level FSM traversal algorithm. 
Chapter \ref{ch:normal} explores the application of FSM traversal algorithm on 
functional verification of sequential GF arithmetic circuits. Chapter \ref{ch:UNSAT} describes
algorithmic techniques to derive UNSAT cores of polynomial
ideals. It also demonstrates with the help of an example how abstraction via
UNSAT cores in algebraic geometry can simplify BMC. 
Chapter \ref{ch:conclude} concludes the dissertation and outlines potential future research for
continuation of this work.
